Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
minor changes

A discrete-time linear system is said to be Bounded-Input and Bounded-Output
(BIBO) stable if and only if every pole of its transfer function lies inside
the unit circle.  \textcolor{red}{Analyzing Eq.~\eqref{eq:outputfunctions}, the following lemma
states necessary conditions for BIBO stability of closed-loop system in
Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$,
$\nu_{1}$, and $\nu_{2}$ are bounded.}

@@

The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for
synthesis of digital controllers able to stabilize closed loop system,
considering plant parametric uncertainties ({\it i.e.}, $\Delta_p \vec{G}$),
quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital
controllers.  Based on it, the model for plant uncertainty due quantisation
noise ({\it i.e.}, $\Delta_q \vec{G}$) may be disregarded if the conditions
on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise
is bounded.  The quantisation noise is indeed bounded, since the following
assumption~\ref{whitenoise} and the Lemmas~\ref{lemma:variance}
and~\ref{lemma:boundednoise} are true.

>>>>

A discrete-time linear system is said to be Bounded-Input and Bounded-Output
(BIBO) stable if and only if every pole of its transfer function lies inside
the unit circle.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following lemma
states necessary conditions for BIBO stability of closed-loop system in
Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$,
$\nu_{1}$, and $\nu_{2}$ are bounded.

@@

The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for
synthesis of digital controllers able to stabilize closed loop system,
considering plant parametric uncertainties ({\it i.e.}, $\Delta_p \vec{G}$),
quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital
controllers.  Based on it, the model for plant uncertainty due quantisation
noise ({\it i.e.}, $\Delta_q \vec{G}$) may be disregarded if the conditions
on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise
is bounded.  The quantisation noise is indeed bounded, since the following
assumption~\ref{whitenoise}.
